### Libraries
```{r libraries, message=FALSE, warning=FALSE}
library(plyr)
library(pracma)
library(dplyr)
library(tidyr)
library(reshape2)
library(stringr)
library(zoo)
library(DBI)
library(RMySQL)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(grid)
library(KernSmooth)
library(cowplot)
```

### Directories
```{r sourceCode}
# Set working directory
setwd("C:/Users/warnold/Local/repos/callite-decision-scaling/runbook")

# load callite input source code
source(file.path('..','src','func_callite_input.R'))

# Set run directory
runDir <- file.path('..','Run')

# Set CalLite program path (must be full path)
calliteV3 <- "C:\\CalLite_v3_64bit"

# Location of monthly 9 addt'l, 11 observed, and 12 rim stations
# simulated by SAC-SMA-DS
simulatedMonthlyDir <- "C:\\Users\\warnold\\California Department of Water Resources\\DWR-EXT-PROJ-SJ Basinwide Study - General\\06_Models\\01_CalLite-WS\\99a_DS_CalLite_Pre-Processing\\climate-change-sim"

# Location of daily baseline gridded data
climData <- file.path("C:\\Users\\warnold\\California Department of Water Resources\\DWR-EXT-PROJ-SJ Basinwide Study - General\\06_Models\\00_WeatherGenerator\\01_Baseline_and_Perturbations\\1")

# DB connection
con <- dbConnect(MySQL(), host='127.0.0.1', port=888,
                 user= "admin", password="climatehawk",
                 dbname="sjv-studies")
# Set location for CalLite Inputs (output from this script)
calliteRuns <- file.path(runDir)

# Set Java Python HEC directory
javaPy <- file.path('..','src','python')

# Set HEC DSS Vue exe directory
my_dss_vue <- file.path("C:\\Users\\warnold\\AppData\\Local\\Programs\\HEC-DSSVue 2.0.1")
```

### Simulation Config
```{r}
################################################################################################################
runName <- "sjv_base_fixed_fmsjsim"  # descriptive (unique) name for runs under consistent assumptions and hydrology
perturbY <- "T_lev"             # currently always "T_lev"
perturbX <- "P_lev"            # "P_lev" or "SD_lev" (set perturbation framework)
calLiteInputDir <- file.path(calliteRuns,runName)
defaultInputDir <- file.path(calLiteInputDir,'Default')
defTableDir <- file.path(defaultInputDir,"Default_Tables")
defDSSDir <- file.path(defaultInputDir,"Default_DSS")
wytAdap <- F
hydrology <- "sjv_base"
################################################################################################################
SLRType <- "BaseCase"   # Select from "0SLR", "15SLR", "30SLR", "45SLR", "60SLR" or "BaseCase"
################################################################################################################
warmingType <- 'Mono'   # "Dist" or "Mono"
forecastCase <- 'base'  # "max" or "base"
sacTempTrigger <-  12   # air temp trigger in degree C, 12 C in default run
calLiteRunCount <- 2   # number of individual CalLite model runs per perturbation
modelYears <- 50        # number of years for each individual CalLite model
writeForecastToDB <- F  # whether to output forecast lookup tables to db
################################################################################################################
```

### Perturbation List
```{r}
# Create incremental perturbation lookup list
cc<-c(1,6:20)
```


### Unpack Pyhton/Java/Jython for text to DSS creation
YOU ONLY NEED TO RUN THIS ONCE 
```{r runDirectorySetup, message=FALSE, warning=FALSE}
# Java HEC Jython for DSS Manipulation
unzip(file.path(javaPy,'vistaHECjythonJava.zip'),
      exdir=file.path(javaPy))
```

### Unpack External DLLs
YOU ONLY NEED TO RUN THIS ONCE
```{r runDirectorySetup, message=FALSE, warning=FALSE}
# Java HEC Jython for DSS Manipulation
unzip(file.path('..','src','Run','External','External.zip'),
      exdir=file.path('..','src','Run','External'))
```

### Unpacks default DSS creation
YOU ONLY NEED TO RUN THIS ONCE PER NEW PROJECT / RUN DIRECTORY
```{r runDirectorySetup, message=FALSE, warning=FALSE}
# Extract default model tables to run directory
unzip(file.path('..','Default.zip'),
      exdir=file.path(runDir,runName,"Default"))
```

### Load Simulated Hydrology (SAC-SMA-DS) to Database
YOU ONLY NEED TO RUN THIS ONCE PER RUN (A UNIQUE SET OF INFLOWS)
If you are adding a different inflow set to the database, rename the older tables so that they are not inadvertently overwritten: e.g. "sim_add9stations" rename to "sim_add9stations_pSac_distTemp"
The 01-Create-CalLite-Runs script will use the default naming (e.g. "sim_add9stations") so make sure to use the correct set that is consistent with the run you are doing.
```{r loadsimhydro, message=FALSE, warning=FALSE}
perturbDIR <- list.dirs(simulatedMonthlyDir)
stationsToDatabase(perturbDIR[2:25], con,
  "sim_add9stations", "sim_obs11stations", "sim_rim12stations",
  'SACSMA_Inflow_CalLite_9.txt', 'SACSMA_Inflow_CalLite_11.txt', 'SACSMA_Inflow_CalLite_12.txt', 
  hydrology)
```

