# CalLite Input Generation

## Source Code
```{r sourceCode}
source(file.path('..','src','func_callite_input.R'))
source(file.path('..','src','func_flow_indices.R'))
source(file.path('..','src','func_warm.R'))
source(file.path('..','src','func_quantile_mapping.R'))
```


## Lookup and Reference Files Setup
### Sacramento Temperature Operations (Table 10)
```{r sacAirportTemp, paged.print=TRUE, warning=FALSE}
sacAirpTempHist <-
  read.table(file = file.path(climData,'meteo_38.65625_-121.53125'),
             col.names = c("YEAR", "MONTH", "DAY", "PRCP", "TAVG")) %>%
  filter(MONTH %in% c(12, 1, 2, 3, 4, 5)) %>%
  mutate(., YEAR = ifelse(MONTH ==12, YEAR+1,YEAR)) %>%
  group_by(YEAR, MONTH) %>% 
  summarise_all(funs(mean))
sacAirpTempHist <- sacAirpTempHist[,c("YEAR", "MONTH", "TAVG")]
dbWriteTable(con, "ref_SAC_temp", sacAirpTempHist, overwrite=T, row.names=FALSE)
sacAirpTempAll <- vector("list",length = length(tChangeList))
for (i in 1:length(tChangeList)) {
  sacAirpTempAll[[i]] <-
    warm(sacAirpTempHist, warmingType,  as.double(gsub('_','.',tChangeList[i])))
}
remove(i)
#sacAirpTempAll[[1]]
```

### Forecast Error Random Variable
```{r randomForecast}
set.seed(1) #specifies the initial value of the random-number seed used by the random-number functions
randForecast <- vector("list", length = calLiteRunCount)
randForecast <- lapply(randForecast, function(x) {
  x <- data.frame(Month = rep(1:5, modelYears),
                                  Year = rep(1922:(1921 + modelYears), each = 5),
                                  Rand_num = runif(5 * modelYears, 0, 1))}
)
#randForecast[[1]]
```

### Default CalLite DSS
```{r dssCreate}
dssIn <- dssCreate(defDSSDir)
#dssIn[,1:10]
```

### Get historical streamflow data
- Historical values for 11 stations on which water year types are based. Units are MAF. Data coverage is from Jan 1922 through Sep 2014 - only use these to determine water year type, so no need to trim.
- Historical values for additional 9 modeled stations - units are TAF.
- Historical values for 12 rim inflows - units are a mix of cfs and TAF. They come directly from the dss input file. Data coverage is from Oct 1921 through Sep 2003. 

```{r loadHist12and9stations}
# 11 stations for water year typing
wytStationsHist <- dbReadTable(con,'ref_11stations_historical')
# Combine 12 rim inflows and 9 additional subbasins into 1 dataframe
# Keep in mind that the add_stations have a longer period 
# of record than the rim inflow stations from the dssIn
mainNodesHist <- cbind(dbReadTable(con,'ref_9stations_historical')[-(985:1068),], 
                       dbReadTable(con,'ref_12stations_historical_callite')[,-(1:2)], 
                       dbReadTable(con,'ref_11stations_historical')[-(985:1116),-(1:2)])
#mainNodesHist
```

### Correlations for Quantile Mapping and WY Typing
Calculate water year type for historical period done for historical run; no need to do it here. Calculate the water year type averages using dssIn. these csv's created for the historic run in the code **"cal drought analysis v4_historical.R"**

Calculate correlations between the rim stations, the 9 additional stations, and the water year type averages, with all dss inputs. Take the rim stations from the dssInput. Get the 9 additional  stations over historic period from California Unimpaired Flow data. This csv created for the historic run in the code **"cal drought analysis v4_historical.R"**
```{r message=TRUE, warning=FALSE, include=FALSE}
# Get nodes which are not correlated to Sac or SJ WY Types
inputsCorr <- dbGetQuery(con,
  paste('SELECT Time_Series AS dssInput, MAX_R2 AS r2, MAX_NAME as corrFlow',
        "FROM `ref_corr_output_calibrate1950-2000`",
        'WHERE MAX_NAME <> "SJWYT" AND MAX_NAME <> "SacWYT"'))
# Get list of correlated dss inputs for Sacramento and SJ water year type mapping
inputsWYTSac <- dbGetQuery(con,paste('SELECT Time_Series AS dssInput',
                                            'FROM `ref_corr_output_calibrate1950-2000`',
                                            'WHERE MAX_NAME = "SacWYT"'))
inputsWYTSJ <- dbGetQuery(con,paste('SELECT Time_Series AS dssInput',
                                            'FROM `ref_corr_output_calibrate1950-2000`',
                                            'WHERE MAX_NAME = "SJWYT"'))
inputsWYTSac <- paste0("`",inputsWYTSac$dssInput,"`", collapse=", ")
inputsWYTSJ <- paste0("`",inputsWYTSJ$dssInput,"`", collapse=", ")
```

### Lookup Tables
Load default lookup tables for CalLite
```{r}
table1 <- read.table(file.path(defTableDir,"x2days.table"),header = T,skip = 3)
table2 <- read.table(file.path(defTableDir,"eightriver.table"),header = T,skip = 2)
table3 <- read.table(file.path(defTableDir,"SacValleyIndex.table"),header = T,skip = 3)
table4 <- read.table(file.path(defTableDir,"wytypeSJR.table"),header = T,skip = 9)
table5 <- read.table(file.path(defTableDir,"wytypeSJRave5.table"),header = T,skip = 4)
table6 <- read.table(file.path(defTableDir,"FebEiRatio.table"),header = T,skip = 2)
table7 <- read.table(file.path(defTableDir,"delta_index.table"),header = T,skip = 2)
table8 <- read.table(file.path(defTableDir,"wytypes.table"),header = T,skip =11)
table9 <- read.table(file.path(defTableDir,"wytypeTRIN.table"),header = T,skip = 1)
table10 <- read.table(file.path(defTableDir,"FWS_BO_A3_Temp.table"),header = T,skip = 8)
table11 <- read.table(file.path(defTableDir,"american_runoff_forecast.table"),header = T,skip = 3)
table12 <- read.table(file.path(defTableDir,"feather_runoff_forecast.table"),header = T,skip = 2)
table13 <- read.table(file.path(defTableDir,"sacramento_runoff_forecast.table"),header = T,skip = 3)
table14 <- read.table(file.path(defTableDir,"UIFR.table"),header = T,skip = 4)
table15 <- read.table(file.path(defTableDir,"AR_B120.table"),header = T,skip = 3)
table16 <- read.table(file.path(defTableDir,"WIIN_wetness.table"),header = T,skip = 4)

```

### Pathnames for Writing CalLite DSS
```{r}
pathnames <- dbGetQuery(con,paste("SELECT * FROM ref_pathnames"))
```

## Loop Perturbations
```{r}
# drop tables that are appended when running the loop
check <- dbExecute(con,paste("DROP TABLE IF EXISTS",paste0("sim_wyTyping_",runName)))
if(writeForecastToDB == T) {
  check <- dbExecute(con,paste("DROP TABLE IF EXISTS",paste0("sim_forecastAmerican_",runName)))
  check <- dbExecute(con,paste("DROP TABLE IF EXISTS",paste0("sim_forecastFeather_",runName)))
  check <- dbExecute(con,paste("DROP TABLE IF EXISTS",paste0("sim_forecastShasta_",runName)))
}
```

```{r message=FALSE, warning=FALSE}
for (p in c(4:4)) {
  for (t in c(1:1)) {
    #Set run directory
    pChangeVal = pChangeList[[p]]; pChangeName = names(pChangeList)[p]
    tChangeVal = tChangeList[[t]]; tChangeName = names(tChangeList)[t]
    ptRunFolder <- paste0(pChangeName, "DP", tChangeName, "DT")
    print(ptRunFolder)
    
    #Create a directory to hold CalLite inputs for the perturbation
    suppressWarnings(calliteInputDirCreate(ptRunFolder,calLiteInputDir))
    
    # Station Sim
    obs11stations <- stationRead(pChangeVal,tChangeVal,con,
                                 calLiteRunCount,modelYears,
                                 paste0('sim_obs11stations_',hydrology,'_maf'), 
                                 paste("Year,","Month,","AMF,","BLB,","BND,","FTO,",
                                       "MRC,","SIS,","SJF,","SNS,","TLG,","TNL,","YRS,","PNF"),TRUE)
    
    add9stations <- stationRead(pChangeVal,tChangeVal,con,
                                calLiteRunCount,modelYears,
                                 paste0('sim_add9stations_',hydrology,'_taf'), 
                                 paste("Year,","Month,","BearRiver,","CacheCreek,",
                                                "CalaverasRiver,","ChowchillaRiver,",
                                                "CosumnesRiver,","FresnoRiver,",
                                                "MokelumneRiver,","PutahCreek,","StonyCreek"),TRUE)

    rim12stations <- stationRead(pChangeVal,tChangeVal,con,
                                 calLiteRunCount,modelYears,
                                 paste0('sim_rim12stations_',hydrology),
                                 paste("I_FOLSM,","I_MCLRE,","I_MELON,","I_MLRTN,",
                                                "I_MOKELUMNE,","I_NHGAN,","I_OROVL,","I_PEDRO,",
                                                "I_SHSTA,","I_TRNTY,","I_YUBA,","I_WKYTN"),FALSE)
    
    # WY Typing 
    wytResults <- wyTyping(pChangeVal,tChangeVal,
                     sac_aji=0.4,sac_omi=0.3,sac_c=5.4,sac_d=6.5,sac_bn=7.8,sac_an=9.2,sac_w=9.2,
                     sj_aji=0.6,sj_omi=0.2,sj_c=2.1,sj_d=2.5,sj_bn=3.1,sj_an=3.8,sj_w=3.8,
                     con,calLiteRunCount,runName,modelYears,obs11stations,dbWrite=TRUE)

    # Quantile Mapping
    dssInQmapped <- qMapping(calLiteRunCount,inputsCorr,dssIn,
                              add9stations, obs11stations, rim12stations, mainNodesHist)

    # WYT
    dssInWYTyped <- wytMapping(inputsWYTSac,inputsWYTSJ,pChangeVal,tChangeVal,
                           con,calLiteRunCount,modelYears,runName)

    # DSS new
    dssInNew <- dssNew(calLiteRunCount,dssIn,dssInWYTyped,dssInQmapped)
    writeDSS(pathnames,file.path(calLiteInputDir,ptRunFolder,"DSS"),
             dssInNew,calLiteRunCount)

    # Tables
    table1new <- table1create(con,calLiteRunCount,modelYears,table1,wytResults,obs11stations)
    table2new <- table2create(calLiteRunCount,modelYears,table2,obs11stations)
    table3new <- table3create(calLiteRunCount,modelYears,table3,wytResults)
    table4new <- table4create(calLiteRunCount,modelYears,table4,wytResults)
    table5new <- table5create(calLiteRunCount,modelYears,table4new,table5)
    table6new <- table6create(con,calLiteRunCount,modelYears,table6,obs11stations)
    table7new <- table7create(calLiteRunCount,modelYears,table7,wytResults)
    table8new <- table8create(calLiteRunCount,modelYears,table8,wytResults)
    table9new <- table9create(calLiteRunCount,modelYears,table9,wytResults)
    table10new <- table10create(calLiteRunCount,modelYears,
                           table10,sacAirpTempAll,sacTempTrigger,t)
    table11new <- table11create(con,calLiteRunCount,modelYears,
                            table11,obs11stations,wytStationsHist,randForecast,forecastCase)
    table12new <- table12create(con,calLiteRunCount,modelYears,
                            table12,obs11stations,wytStationsHist,randForecast,forecastCase)
    table13new <- table13create(con,calLiteRunCount,modelYears,
                            table13,obs11stations,wytStationsHist,randForecast,forecastCase)
    table14new <- table14create(calLiteRunCount,modelYears,table14,wytResults)
    table15new <- table15create(calLiteRunCount,modelYears,table15,wytResults)
    
    # Lookup Tables
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "x2days",table1new,file.path(defTableDir,"x2days.table"),3)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "eightriver",table2new,file.path(defTableDir,"eightriver.table"),2)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "SacValleyIndex",table3new,file.path(defTableDir,"SacValleyIndex.table"),3)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "wytypeSJR",table4new,file.path(defTableDir,"wytypeSJR.table"),9)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "wytypeSJRave5",table5new,file.path(defTableDir,"wytypeSJRave5.table"),4)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "FebEiRatio",table6new,file.path(defTableDir,"FebEiRatio.table"),2)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "delta_index",table7new,file.path(defTableDir,"delta_index.table"),2)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "wytypes",table8new,file.path(defTableDir,"wytypes.table"),11)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "wytypeTRIN",table9new,file.path(defTableDir,"wytypeTRIN.table"),1)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "FWS_BO_A3_Temp",table10new,file.path(defTableDir,"FWS_BO_A3_Temp.table"),8)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "UIFR",table14new,file.path(defTableDir,"UIFR.table"),4)
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
               "AR_B120",table14new,file.path(defTableDir,"AR_B120.table"),3)

    # Forecast Tables
    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"New_ForecastTables"),
               "american_runoff_forecast",table11new,
               file.path(defTableDir,"american_runoff_forecast.table"),3)


    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"New_ForecastTables"),
               "feather_runoff_forecast",table12new,
               file.path(defTableDir,"feather_runoff_forecast.table"),2)


    writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"New_ForecastTables"),
               "sacramento_runoff_forecast",table13new,
               file.path(defTableDir,"sacramento_runoff_forecast.table"),3)

    if(writeForecastToDB == T) {
      writeDB(pChangeVal,tChangeVal,con,calLiteRunCount,modelYears,
                            table11new,runName,4,c(2,3,4,5),'forecastAmerican',FALSE)
      writeDB(pChangeVal,tChangeVal,con,calLiteRunCount,modelYears,
                            table13new,runName,4,c(2,3,4,5),'forecastShasta',FALSE)
      writeDB(pChangeVal,tChangeVal,con,calLiteRunCount,modelYears,
                            table12new,runName,5,c(1,2,3),'forecastFeather',TRUE)
    }
    
  }
}

```

# WYT Adaptation (Modifies Lookup Tables for WYT)
```{r}
for (p in c(4:4)) {
  for (t in c(1,3,5,7,9)) {
    #Set run directory
    pChangeVal = pChangeList[[p]]; pChangeName = names(pChangeList)[p]
    tChangeVal = tChangeList[[t]]; tChangeName = names(tChangeList)[t]
    
    # Station Sim
    obs11stations <- stationRead(pChangeVal,tChangeVal,con,
                                 calLiteRunCount,modelYears,
                                 paste0('sim_obs11stations_',hydrology,'_maf'), 
                                 paste("Year,","Month,","AMF,","BLB,","BND,","FTO,",
                                       "MRC,","SIS,","SJF,","SNS,","TLG,","TNL,","YRS"),TRUE)
    
    # WY Typing
    sql <- paste('select * from ref_wyt_adap where dt=',tChangeVal,
                 'and dp=',pChangeVal,'and index_name="sac"')
    res <- dbSendQuery(con,sql)
    sac_wyt <- dbFetch(res)
    
    sql <- paste('select * from ref_wyt_adap where dt=',tChangeVal,
                 'and dp=',pChangeVal,'and index_name="sj"')
    res <- dbSendQuery(con,sql)
    sj_wyt <- dbFetch(res)
    
    wytResults <- wyTyping(pChangeVal,tChangeVal,
                     sac_wyt$aji/100,sac_wyt$omi/100,
                     sac_wyt['D-C'],sac_wyt['BN-D'],sac_wyt['AN-BN'],sac_wyt['W-AN'],sac_wyt['W-AN'],
                     sj_wyt$aji/100,sj_wyt$omi/100,
                     sj_wyt['D-C'],sj_wyt['BN-D'],sj_wyt['AN-BN'],sj_wyt['W-AN'],sj_wyt['W-AN'],
                     con,calLiteRunCount,runName,modelYears,obs11stations,dbWrite=TRUE)


    # Tables
    table4new <- table4create(calLiteRunCount,modelYears,table4,wytResults)
    table5new <- table5create(calLiteRunCount,modelYears,table4new,table5)
    table8new <- table8create(calLiteRunCount,modelYears,table8,wytResults)
    
    # Lookup Tables
    for (SLRType in slrChangeList) { 
      ptRunFolder <- paste0(pChangeName, "DP", tChangeName, "DT", SLRType)
      #Create a directory to hold CalLite inputs for the perturbation
      suppressWarnings(calliteInputDirCreate(ptRunFolder,calLiteInputDir))
      print(ptRunFolder)
      
      writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
                 "wytypeSJR_adap",table4new,file.path(defTableDir,"wytypeSJR_adap.table"),9)
      writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
                 "wytypeSJRave5_adap",table5new,file.path(defTableDir,"wytypeSJRave5_adap.table"),4)
      writeTable(calLiteRunCount,file.path(calLiteInputDir,ptRunFolder,"Lookup_Tables"),
                 "wytypes_adap",table8new,file.path(defTableDir,"wytypes_adap.table"),11)
    }
  }
}

```

